Reprint Authors per Country

### 2019-10-22 analysis/001_kb_rp_pretest.Rmd
comment to data consistency #2
check author id and re-render notebook #2

@@

Corresponding authors work in different countries. For `UT_EID=000372645900002`, the Web of Science lists two corresponding authors, one affilated with a Spanish, the other with a Portuguese institution. As in Examples 1 and 2, only one affiliation is tagged with RP in `wos_b_2019.items_author_institutions`. Moreover, checking the WoS raw data reveals that the RP-author `14734495` is not affiliated with an Portuguese institution at all. <!--when I run the query it only shows 10 records, none of them has fk_author 14734495-->

>>>>

because I was not aware of this issue before. Let's wait and see how the table will be changed after the KB realised this data consistency issue.

@@

Corresponding authors work in different countries. For `UT_EID=000372645900002`, the Web of Science lists two corresponding authors, one affilated with a Spanish, the other with a Portuguese institution. As in Examples 1 and 2, only one affiliation is tagged with RP in `wos_b_2019.items_author_institutions`. Moreover, checking the WoS raw data reveals that the RP-author `15145104` is not affiliated with an Portuguese institution at all.
